Q1: Are lake and terrestrial primary productivity coherent?

### 2020-07-01 AnalysisCode/Q1_CoherenceVariation/ms1_analyses_rf_to_gam_IWSnotHU12_20200312.Rmd
revisions post review

gam.cohst<-gam(accndvicoh.ts1 ~ s(hu12_dep_totaln_tavg_mean) + s(cv.accndvi) + s(iws_nlcd2011_pct_90,k=3)
               #+ s(wlconnections_allwetlands_shoreline_km) + s(hu12_runoff_mean)
               , data=rfdat.cohst, gamma=1, weights=lwgt)
gam.check(gam.cohst)
concurvity(gam.cohst,full=F)$estimate
summary(gam.cohst)
plot(rfdat.cohst$accndvicoh.ts1, predict(gam.cohst, rfdat.cohst))

@@

gam.cohlt<-gam(accndvicoh.ts2 ~ s(iws_nlcd2011_pct_52) + s(cv.accndvi) + 
                 s(iws_wl_regimefwetlandsundissolved_overlapping_area_pct) 
               #+  s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean) + s(wlconnections_forestedwetlands_shoreline_km)
               , data=rfdat.cohlt, gamma=1, weights=lwgt)
gam.check(gam.cohlt)
concurvity(gam.cohlt,full=F)$estimate
summary(gam.cohlt)
plot(rfdat.cohlt$accndvicoh.ts2, predict(gam.cohlt, rfdat.cohlt))

@@

#cosine
gam.cosphist<-gam(cos(accndviphi.ts1) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
                  s(chla) + s(iws_nlcd2011_pct_52,k=3), data=rfdat.phist, gamma=1, weights=lwgt)
gam.check(gam.cosphist)
concurvity(gam.cosphist, full=F)$estimate
summary(gam.cosphist)
plot(cos(rfdat.phist$accndviphi.ts1), predict(gam.cosphist, rfdat.phist))

@@

#sine
gam.sinphilt<-gam(sin(accndviphi.ts2) ~ s(wlconnections_openwaterwetlands_shoreline_km) + 
                 s(iws_nlcd2011_pct_82) + s(iws_wl_regimefwetlandsundissolved_overlapping_area_pct), 
               data=rfdat.philt, gamma=1, weights=lwgt)
gam.check(gam.sinphilt)
concurvity(gam.sinphilt,full=F)$estimate
summary(gam.sinphilt)
plot(sin(rfdat.philt$accndviphi.ts2), predict(gam.sinphilt, rfdat.philt))

@@

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_bycolumn_iws.tif",units="in",res=300,width=bigwd, height=bight)

@@

# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
# rasterImage(image=panel5a,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="total N deposition",ylab="short coherence", ylim=c(-.6,.6))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"a)")
plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="short coherence", ylim=c(-.6,.6))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"b)")
plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% woody wetlands",ylab="",ylim=c(-.6,.6))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"c)")
#plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetlands shoreline",ylab="",ylim=c(-.6,.6))
# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"d)")
# plot(gam.cohst,select=5,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean runoff",ylab="",ylim=c(-.6,.6))
# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"e)")

plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetld. shoreline",ylab="short phase")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"d)")
plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean chlorophyll-a",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"e)")
plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"f)")
# plot.new()
# plot.new()

# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
# rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-.6,.6))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"g)")
plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="cv(NDVI)",ylab="long coherence",ylim=c(-.6,.6))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"h)")
plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% regime f wetlands",ylab="",ylim=c(-.6,.6))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"i)")
# plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean annual precipitation",ylab="", ylim=c(-.6,.6))
# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"l)")
# plot(gam.cohlt,select=5,residuals=T,rug=FALSE,shade=T,cex=2,xlab="forest wetlands shoreline",ylab="",ylim=c(-.6,.6))
# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"m)")

# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-4 sub-region",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
# rasterImage(image=panel5n,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,cex=2,xlab="open wetld. shoreline",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"j)")
plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% cultivated crops",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"k)")
plot(gam.sinphilt,select=3,residuals=T,rug=FALSE,shade=T,cex=2,xlab="% regime f wetlands",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"l)")

>>>>

gam.cohst<-gam(accndvicoh.ts1 ~ s(hu12_dep_totaln_tavg_mean) + s(log10(cv.accndvi)) + s(iws_nlcd2011_pct_90,k=3)
               #+ s(wlconnections_allwetlands_shoreline_km) + s(hu12_runoff_mean)
               , data=rfdat.cohst, gamma=1, weights=lwgt, family=betar)
gam.check(gam.cohst)
concurvity(gam.cohst,full=F)$estimate
summary(gam.cohst)
plot(rfdat.cohst$accndvicoh.ts1, predict(gam.cohst, rfdat.cohst))

@@

gam.cohlt<-gam(accndvicoh.ts2 ~ s(iws_nlcd2011_pct_52) + s(log10(cv.accndvi)) + 
                 s(iws_wl_regimefwetlandsundissolved_overlapping_area_pct) 
               #+  s(hu12_prism_ppt_30yr_normal_800mm2_annual_mean) + s(wlconnections_forestedwetlands_shoreline_km)
               , data=rfdat.cohlt, gamma=1, weights=lwgt, family="betar")
gam.check(gam.cohlt)
concurvity(gam.cohlt,full=F)$estimate
summary(gam.cohlt)
plot(rfdat.cohlt$accndvicoh.ts2, predict(gam.cohlt, rfdat.cohlt))

@@

#cosine
gam.cosphist<-gam(cos(accndviphi.ts1) ~ s(sqrt(wlconnections_openwaterwetlands_shoreline_km),k=3) + 
                  s(log10(chla)) + s(iws_nlcd2011_pct_52,k=3), data=rfdat.phist, gamma=1, weights=lwgt)
gam.check(gam.cosphist)
concurvity(gam.cosphist, full=F)$estimate
summary(gam.cosphist)
plot(cos(rfdat.phist$accndviphi.ts1), predict(gam.cosphist, rfdat.phist))

@@

#sine
gam.sinphilt<-gam(sin(accndviphi.ts2) ~ s(sqrt(wlconnections_openwaterwetlands_shoreline_km)) + 
                 s(iws_nlcd2011_pct_82) + s(sqrt(iws_wl_regimefwetlandsundissolved_overlapping_area_pct)), 
               data=rfdat.philt, gamma=1, weights=lwgt)
gam.check(gam.sinphilt)
concurvity(gam.sinphilt,full=F)$estimate
summary(gam.sinphilt)
plot(sin(rfdat.philt$accndviphi.ts2), predict(gam.sinphilt, rfdat.philt))

@@

tiff("~/Box Sync/NSF EAGER Synchrony/Manuscripts/1_CoherenceSpatialVariation/fig5_gamfits_bycolumn_iws_v2.tif",units="in",res=300,width=bigwd, height=bight)

@@

# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
# rasterImage(image=panel5a,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
plot(gam.cohst,select=1,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="total N deposition",ylab="short coherence", ylim=c(-2,3.2))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"a)")
plot(gam.cohst,select=2,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab=expression(paste("log"[10],"(cv(NDVI))",sep="")),ylab="short coherence", ylim=c(-2,3.2))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"b)")
plot(gam.cohst,select=3,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="% woody wetlands",ylab="",ylim=c(-2,3.2))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"c)")
#plot(gam.cohst,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="all wetlands shoreline",ylab="",ylim=c(-.6,.6))
# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"d)")
# plot(gam.cohst,select=5,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean runoff",ylab="",ylim=c(-.6,.6))
# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"e)")

plot(gam.cosphist,select=1,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="sqrt(open wetld. shoreline)",ylab="short phase")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"d)")
plot(gam.cosphist,select=2,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab=expression(paste("log"[10],"(mean chlorophyll-a)",sep="")),ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"e)")
plot(gam.cosphist,select=3,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="% shrub/scrub",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"f)")
# plot.new()
# plot.new()

# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-8 sub-basin",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
# rasterImage(image=panel5i,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
plot(gam.cohlt,select=1,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="% shrub/scrub",ylab="long coherence",ylim=c(-2.5,2.2))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"g)")
plot(gam.cohlt,select=2,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab=expression(paste("log"[10],"(cv(NDVI))",sep="")),ylab="long coherence",ylim=c(-2.5,2.2))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"h)")
plot(gam.cohlt,select=3,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="% regime f wetlands",ylab="",ylim=c(-2.5,2.2))
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"i)")
# plot(gam.cohlt,select=4,residuals=T,rug=FALSE,shade=T,cex=2,xlab="mean annual precipitation",ylab="", ylim=c(-.6,.6))
# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"l)")
# plot(gam.cohlt,select=5,residuals=T,rug=FALSE,shade=T,cex=2,xlab="forest wetlands shoreline",ylab="",ylim=c(-.6,.6))
# text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"m)")

# plot(NA,NA,xlim=c(0,1),ylim=c(0,1),xaxs="i",yaxs="i",ylab="",xlab="HUC-4 sub-region",xaxt="n",yaxt="n",mgp=c(1,0.5,0))
# rasterImage(image=panel5n,xleft=1e-2,ybottom=1e-2,xright=1-1e-2,ytop=1-1e-2)
plot(gam.sinphilt,select=1,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="sqrt(open wetld. shoreline)",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"j)")
plot(gam.sinphilt,select=2,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="% cultivated crops",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"k)")
plot(gam.sinphilt,select=3,residuals=T,rug=FALSE,shade=T,pch=20,cex=.2,xlab="sqrt(% regime f wetlands)",ylab="")
text(par("usr")[1]+0.075*diff(par("usr")[1:2]), par("usr")[4]-0.075*diff(par("usr")[3:4]),"l)")
